\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-26 src/tex/ms.tex
Finishing Kaze's edit

Every waveform approximants have some fitting coefficients that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are 209 fitting coefficients used to capture the separate
behavior of the amplitude and phase as a function of the mass ratio and spins.
The accuracy of fitting coefficients determines how well the approximant
reproduces the NR waveform. The inaccuracy in obtaining the fitting coefficients
means misrepresentation of the NR waveform, meaning the use of approximant will
introduce some systematic error in downstream data analysis task. For example,
this would mean the recovered source parameters will be biased in the case of PE.
\kw{Say something about how the fitting parameters affect the accuracy of the waveform model}

% Motivation
\kw{Motivate the need for improving the fitting process by joint fit.}

Previously in the construction of IMRPhenomD \citep{Khan:2015jqa}, waveform
coefficients are fitted in segments with amplitude and phase separated.
Individual segments are then connected together such that they are
differentiable. Using this method, the generated waveforms are expected to be
erroneous, as the connections would affect the originally fitted segments. The
coefficients of the current IMRPhenomD implementation are often hand tuned, and
are tuned in sub-sets of parameters instead of all together. This means the
tuning process ignore the correlation between different sub-sets of parameters,
so the best-fitted solution obtained by fitting sub-sets of parameters may not
be the global optimum compared to fitting all coefficients at once. Instead, by
jointly fitting all coefficients, the inaccuracy in fitting individual and
connecting different segments can be accounted during the optimization.
Therefore, there is potential accuracy one can gain by fitting all coefficients
at once.

Since we can differentiate through the entire waveform model against the fitting
parameters, one can use gradient descent to find the optimal fitting parameters
all at once instead of fitting them in subsets.

@@

With further modifications to the optimization process, the set of waveform coefficients can be retuned to give almost an order-of-magnitude improvement. 
Utilizing AD, differentiable waveform models can be further improved easily and quickly using similar computational schemes. 
Moreover, in the construction of new waveform models, AD shows significant advantages during their calibrating process.

\subsection{Fisher Forecasting}
\label{subsec:fisher}

>>>>

Every waveform approximants have some fitting coefficients that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are 209 fitting coefficients used to capture the separate
behavior of the amplitude and phase as a function of the mass ratio and spins.
The accuracy of fitting coefficients determines how well the approximant
reproduces the NR waveform. The inaccuracy in obtaining the fitting coefficients
means misrepresentation of the NR waveform, meaning the use of approximant will
introduce some systematic error in downstream data analysis task. For example,
this would mean the recovered source parameters will be biased in the case of PE.

% Motivation
Previously in the construction of IMRPhenomD \citep{Khan:2015jqa}, waveform
coefficients are fitted in segments with amplitude and phase separated.
Individual segments are then connected together such that they are
differentiable. Using this method, the generated waveforms are expected to be
erroneous, as the connections would affect the originally fitted segments. The
coefficients of the current IMRPhenomD implementation are often hand tuned, and
are tuned in sub-sets of parameters instead of all together. This means the
tuning process ignore the correlation between different sub-sets of parameters,
so the best-fitted solution obtained by fitting sub-sets of parameters may not
be the global optimum compared to fitting all coefficients at once. Instead, by
jointly fitting all coefficients, the inaccuracy in fitting individual and
connecting different segments can be accounted during the optimization.
Therefore, there is potential accuracy one can gain by fitting all coefficients
at once.

\kw{Kelvin Fill}
Since we can differentiate through the entire waveform model against the fitting
parameters, one can use gradient descent to find the optimal fitting parameters
all at once instead of fitting them in subsets.

@@

This fine-tuning step is rather simple and general. Given a different
differentiable waveform model, one can apply the same procedure to optimize the
coefficients in the new model, i.e. applying gradient descent to optimize all
the fitting coefficients all together. This provides a more flexible control
during the calibration process, and potentially better final result.
With further modifications to the optimization process, the set of waveform
coefficients can be retuned to give almost an order-of-magnitude improvement.
\kw{Where is the proof for this?} 
\subsection{Fisher Forecasting}
\label{subsec:fisher}
